---
title: "HW_1"
author: "Andus Kong; UNI: ak4479"
date: "9/17/2020"
output: pdf_document
---
## 1. Form Project Teams
We are group 12 in the spreadsheet.  
The UNI's of the group member are as follow:  
1. ak4479  
2. ht2459  
3. sy2657  
4. jc5066  
5. yg2655  

## 2. Read Chapter 1 of Statistical Sleuth
Completed

## 3. Data Questions for Display 1.3

### i) Determine whether there are outliers in the combined data,  using boxplots or other suitable methods.

Using simple boxplots we can see that in the male category there is one salary of 8100 that is above the Upper Limit, which can be considered an outlier.

```{r}
library(Sleuth3)
library(ggplot2)
library(dplyr)
df <- case0102

p <- ggplot(data = df, aes(x = Salary,
                           fill = Sex))
p +geom_boxplot() + coord_flip() + theme(axis.title.x=element_blank(), 
                                         axis.text.x=element_blank(),
                                         axis.ticks.x=element_blank()) +
  labs(title = "Salary by Gender") 

p + geom_histogram(bins = 30) + labs(title = "Histogram of Salary by Gender")
```

### ii) Perform separate EDA, and compute the sample coefficient of variation and median for Salary in each group (i.e., Males and Females)

Below is a table of Standard Deviation, Mean, Coefficient of Variation, and Median of both genders in the data
```{r}
sample_coef <- df %>% group_by(Sex) %>% summarise(SD  = sd(Salary),
                                                  mu = mean(Salary),
                                                  Coeff_var = SD / mu,
                                                  Median = median(Salary))
sample_coef
```

### iii) For each of the estimates computed in (ii) above, determine the bias and variance using each of the following methods:

### A. Jackknife

```{r}

```


### B. Bootstrap

```{r}
library(purrr)
Num_Samples <- 10
K <- 1000
n <- nrow(df)

l <- list()
for(i in 1:Num_Samples){
  boot <- sample(1:n, size = K, replace = TRUE)
  boot_df <- df[boot,]
  boot_coeff <- boot_df %>% group_by(Sex) %>% summarise(SD  = sd(Salary),
                                                  mu = mean(Salary),
                                                  Coeff_var = SD / mu,
                                                  Median = median(Salary))
  l[[i]] <- boot_coeff
}
boot_coeff_combined <- bind_rows(l, .id = "Indicator") %>% select(-"Indicator") %>% group_by(Sex) %>%
  summarise(Coeff_var = mean(Coeff_var),
            Median = mean(Median))
boot_coeff_combined
(boot_coeff_combined %>% select(Coeff_var, Median)) - (sample_coef %>% select(Coeff_var, Median))
```

